CLT item selection

### 2022-05-17 analysis/clt_item_selection.Rmd
add size simulations 100 iter

for (j in 1:5) {

@@

sim_size_age%>%
  ggplot(aes(x = factor(size), y = cor, col = factor(age_group)))+
  geom_point(pch = 1)+
  geom_line(aes(group = interaction(age_group,factor(iter)), lty = factor(iter)))+
  theme_minimal()+
  scale_linetype(name = "Run")+
  #facet_grid(factor(iter)~.)+
  labs(x = "No. of items", y = "Correlation with full test")+
  scale_color_colorblind(name = "Age group")

>>>>

@@

sim_size_age%>%
  group_by(size, age_group)%>%
  summarise(mean_cor = mean(cor),
         min = min(cor),
         max = max(cor))%>%
  ggplot(aes(x = factor(size), y = mean_cor, col = factor(age_group)))+
  geom_pointrange(aes(ymin=min, max = max), pch = 1)+
  geom_line(aes(group = factor(age_group)))+
  theme_minimal()+
  scale_linetype(name = "Run")+
  #facet_grid(factor(iter)~.)+
  labs(x = "No. of items", y = "Correlation with full test")+
  scale_color_colorblind(name = "Age group")
